\documentclass[11pt,letterpaper]{letter}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\usepackage{array}

\signature{Matthew Hoiland}
\address{84 E 200 S, Provo \\
  UT, 84606 \\
  (208) 794-1506 \\
  matthew.hoiland@vivint.com \\
  LinkedIn: mphoiland \\
  GitHub: matt-hoiland}

\begin{document}

\begin{letter}{Bobby Aragon \\
  Niven Wofford \\
  Vivint.SmartHome \\
  3401 Ashton Blvd \\
  Lehi, UT 84043}
\opening{Dear Sirs:}

I am writing to you to apply for the Regression Tester job posting. I am interested in this position as I have already been working in its entry level form since March and have found it very fulfilling.

I am prepared to meet the rising challenges this job presents. As Vivint continues to innovate, I will bring essential skills and values. First, I strive to balance a sharp eye for detail with a greater understanding of context and purpose. Second, I value documentation not as something to be completed but as a means of communication. Finally, my education in software engineering enables me to operate cross-functionally and flexibly.

When I worked as a teaching assistant at BYU's computer science department, I had unique opportunities among my colleagues to work on our suite of testing software which graded the code of hundreds of students per semester. These tests needed to be well designed in coverage, case partitions, boundary conditions, error states, and most importantly accuracy. A challenge I found particularly rewarding was providing actionable feedback to my students based on test results.

I have exercised similar skills in my current position. In addition to my primary responsibilities, I have reviewed our test suites for redundancy, efficiency, and compliance to acceptance criteria. I have also made efforts to network with our automation QA teams. As Vivint's services increase in capacity, our tests suites increase in complexity. I have the inertia, in-house knowledge, and ability to help push us forward.

I am eager to continue this work. Thank you in advance for your consideration. I look forward to hearing from you.

\closing{Gratefully,}

\end{letter}

\end{document}
